---
title: "README"
output:
   html_document:
    keep_md: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pikchr

<!-- badges: start -->
![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/pikchr) &nbsp; 
![CRAN Downloads](https://cranlogs.r-pkg.org/badges/grand-total/pikchr) &nbsp; 
![](https://img.shields.io/badge/devel%20version-0.98-blue.svg)
<!-- badges: end -->


Welcome to the `pikchr` package website, an R interface for the **PIC diagramming language**, powered by the parser from <https://pikchr.org>. The `pikchr` package allows you to create diagrams directly within R, combining simplicity and precision for efficient diagram generation.

With `pikchr`, you can produce complex diagrams for documentation, presentations, articles, and more, all from your R environment. The straightforward nature of the **PIC language**, paired with the power of R, makes this package a valuable tool for those needing precise, customizable visualizations in academic, technical, and scientific projects. Discover how `pikchr` can enhance and streamline your diagramming workflow!

## Installation

You can install directly from CRAN or the development version of pikchr from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("StrategicProjects/pikchr")
```

```{r}
library(pikchr)

pikchr('
/*
basic example code
*/
arrow right 200% "Rmarkdown" "Source" # teste
box rad 10px "Rmarkdown" "(knitr)" bold  fit
arrow right 200% "HTML+SVG" "Output" 
arrow <-> down from last box.s
box same "Pikchr" "(pikchr.c)" bold fit
',
width = "100%",
height = "auto",
align = "center", 
fontFamily = "Flamenco", svgOnly = TRUE)
```


You can also use the `{pikchr}` engine in a `Rmarkdown` document.

```{pikchr}
#| width: 100%
#| height: auto
#| fig.align: center
#| fontFamily: Jost
/*
basic example code in a markdown chunk.
*/
arrow right 200% "Rmarkdown" "Source" 
box rad 10px "Rmarkdown" "(knitr)" bold  fit
arrow right 200% "HTML+SVG" "Output" 
arrow <-> down from last box.s
box same "Pikchr" "(pikchr.c)" bold fit
```

